\documentclass{article}
\input{~/studies/preamble}

\title{Transformer}
\author{Hyoung Joon, Kim}
\date{\today}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Introduction}
    The \textbf{transformer} architecture was originally introduced for NLP (Natural Language Processing)
    , and surpasses the RNN (Residual Neural Network), which was the mainstream of NLP. Transformers can
    process various types of data, even if it was developed for NLP. For example, ViT (vision transformers)
    often outperfrom CNN in image processing tasks.

    Transformers has following merits:
    \begin{itemize}
        \item Effective in transfer learning: The transformer can be trained on large dataset, and then can be fine-tuned for downstream tasks.
        \item Well-suited to massive parallel processors such as GPUs. This accelerates training and inference process of transformers, which RNN cannot do.
        \item Shares parameters, which leads to more efficient memory usage than ordinary full-connected layer.
    \end{itemize}

\section{Main Ideas}
    \subsection{Attention}
        The transformer is based on the \textbf{attention} mechanism. The attention calculates how much the data must
        take \emph{attention} to other data. For example, consider following two sentences:
        \begin{align*}
            &\text{I swam across the river to get to the bank.} \\
            &\text{I walked across the road to get cash from the bank.}
        \end{align*}
        The word \emph{bank} has different interpretation in two sentences, and this difference
        can be found from other words in each setence:
        \begin{itemize}
            \item The meaning of the bank in first sentence can be induced from \emph{swam} and \emph{river}.
            \item The meaning of the bank in second sentence can be induced from \emph{cash}.
        \end{itemize}
        So, to process this sentences, one must estimate the amount of \emph{attention} that words take on each other words.
        
        \subsubsection{Dot-product Self-attention}
            Now we discuss the precise structure of the heart of the transformer architecture, the attention mechanism.

            \begin{defn}{Dot-product Self-attention}{dotProdSelfAtten}
                Let $\textbf{X}$ be $N \times D$ matrix, which consists of $N$ $D \times 1$ data vectors.
                Then, the \textbf{dot-product self-attention} \textbf{Sa}, which is an $N \times D_v$ matrix, is defined as following:
                \[
                \textbf{Sa}[\textbf{X}]=\textbf{Softmax}\left( \textbf{Q}^{\top}\textbf{K}\right)\textbf{V}
                \]
                where \textbf{V}, \textbf{Q}, \textbf{K}, called value, query and key, is defined as following:
                \begin{align*}
                    \textbf{V} &= \textbf{1}^{\top}\bm{\beta}_v + \textbf{X}\textbf{W}_v \\
                    \textbf{Q} &= \textbf{1}^{\top}\bm{\beta}_q + \textbf{X}\textbf{W}_q \\
                    \textbf{K} &= \textbf{1}^{\top}\bm{\beta}_k + \textbf{X}\textbf{W}_k
                \end{align*}
                
                \begin{itemize}
                    \item $\textbf{W}^{(v)}$, $\bm{\beta}_v$ have dimensionality $D \times D_v$ and $D_v \times 1$, respectively.
                    \item $\textbf{W}^{(q)}$, $\bm{\beta}_q$ have dimensionality $D \times D_q$ and $D_q \times 1$, respectively.
                    \item $\textbf{W}^{(k)}$, $\bm{\beta}_k$ have dimensionality $D \times D_k$ and $D_k \times 1$, respectively.
                \end{itemize}
                
                \textbf{1} is an $N \times 1$ row-vector. 
                $D_v$ governs the size of the output vectors.
                The \textbf{Softmax} function applies ordinary softmax function to each row, respectively.
            \end{defn}
            The key represents the information which the value is holding.
            The query represents what value is asking to other values, required to understand its meaning in the whole data.
            If the query and key matches well then the dot product will produce large value.
            If not, the dot product result will be small. This is the 'attention'.

            This is quite unintuitive at first look, so let's get some intuition of these equations.

        \subsubsection{Intuition of the Attention Mechanism}
            The motivation of the attention is to calculate the amount of attention the data pays to every other data,
            which can be expressed as following:
            \[
            \textbf{y}_n = \sum_{m=1}^{N}a_{nm}\textbf{x}_m
            \]
            with data $\{\textbf{x}_1 \dots \textbf{x}_N\}$.
            The $a_{nm}$ is \emph{attention weight}, and we can interpret this as how much the $\textbf{x}_n$ pay attention to $\textbf{x}_m$.
            If $a_{nm}$ is high, then $\textbf{x}_n$ is highly related, or pays attention, to $\textbf{x}_m$.
            If it is not, then the relevancy is low.
            To let the $a_{nm}$ represent the amount of attention in reasonable way, 
            we would like to constrain the attention weights
            in the following way:
            \begin{align*}
                a_{nm} & \geq 0, \\
                \sum_{m=1}^{N}a_{nm} & = 1.
            \end{align*}
            Now, one of the simple way of caculating $a_{nm}$ is to take the dot product of $\textbf{x}_n$ and $\textbf{x}_m$.
            But, we can make it more flexible by introducing the \textbf{query} and \textbf{key} vectors;
            \begin{align*}
                \textbf{q}_n &= \bm{\beta}_q + \textbf{W}_q\textbf{x}_n \\
                \textbf{k}_m &= \bm{\beta}_k + \textbf{W}_k\textbf{x}_m
            \end{align*}

            Now we must caculate how much the query should pay attention to the key value. We use softmax function to meet the requirements we
            considered earlier;
            \[
                a_{nm} = \frac{\exp \textbf{q}_n^\top \textbf{k}_m}
                {\sum_{i=1}^{N} \exp{\textbf{q}_n^\top \textbf{k}_i}}
            \]

            Now we transform the vector $\textbf{x}_m$ to $\textbf{v}_m$, by following equation:
            \[
                \textbf{v}_m = \bm{\beta}_v + \textbf{W}_v\textbf{x}_m
            \]
            where $\bm{\beta}_v$ and $\textbf{W}_v$ are bias and weights, respectively.
            Since the original data can be difficult to directly recognize the relevance, we are transforming it.
            
            So, the final output is
            \[
                \textbf{y}_n = \sum_{m=1}^{N} \frac{\exp \textbf{q}_n^\top \textbf{k}_m}
                {\sum_{i=1}^{N} \exp{\textbf{q}_n^\top \textbf{k}_i}} \textbf{v}_m
            \]

            To summarize, the following are the meaning of each matrices:
            \begin{itemize}
                \item $\textbf{q}_n$: The question that $\textbf{v}_n$ asks to other key.
                \item $\textbf{k}_n$: The information that $\textbf{v}_n$ is holding.
                \item the attention weight $a_{nm} = \dfrac{\exp \textbf{q}_n^\top \textbf{k}_m}{\sum_{i=1}^{N} \exp{\textbf{q}_n^\top \textbf{k}_i}}$
                : the amount of attention that $\textbf{v}_n$ is paying to $\textbf{v}_m$.
                \item $\textbf{y}_n = \sum_{m=1}^{N} \dfrac{\exp \textbf{q}_n^\top \textbf{k}_m}
                {\sum_{i=1}^{N} \exp{\textbf{q}_n^\top \textbf{k}_i}} \textbf{v}_m$: Newly created context which is easier to interpret.
                The amount of attention that $\textbf{v}_n$ is paying to other data is compressed in.
            \end{itemize}

    \subsection{Extensions to Attention}
        The following extensions are used very often when using attention mechanism.
        \subsubsection{Scaled Dot-product Self-attention}
            The dot product in attention mechanism can have large magnitude, and the softmax function will going to produce
            very small gradient value for that dot product result. So we resize the value that softmax function receives by
            dividing with square root of the dimension of query vector (which must be same as key vector's dimension);
            \begin{defn}{Scaled Dot-product Self-attention}{scaledDPSA}
            \[
                \textbf{Sa}[\textbf{X}]=\textbf{Softmax}\left(\frac{\textbf{Q}^{\top}\textbf{K}}{\sqrt{D_k}}\right)\textbf{V}
            \]
            \end{defn}
            This is called \textbf{scaled dot-product self-attention}.
        
        \subsubsection{Multi-head Attention}
            The self-attention mechanism make use of same parameter for each input data.
            This may decrease the expressive power of the attention, and does not consider
            the situation where various context must be used.
            To prevent this, we use multiple value, query, and key weights.
            We produce attention result in parallel with each weights and then concatenate them.
            This is called \textbf{multi-head attention}.
            \begin{defn}{Multi-head Attention}
                Let $\textbf{W}_v^h$, $\textbf{W}_q^h$, and $\textbf{W}_k^h$ be the weights of $h$-th attention mechanism or \textbf{head}.
                Let $\bm{\beta}_v^h$, $\bm{\beta}_q^h$, and $\bm{\beta}_k^h$ be the biases of $h$-th head.
                We calculate $h$-th value, query, and key as:
                \begin{align*}
                    \textbf{V}_h &= \textbf{1}^{\top}\bm{\beta}_v^h + \textbf{X}\textbf{W}_v^h \\
                    \textbf{Q}_h &= \textbf{1}^{\top}\bm{\beta}_q^h + \textbf{X}\textbf{W}_q^h \\
                    \textbf{K}_h &= \textbf{1}^{\top}\bm{\beta}_k^h + \textbf{X}\textbf{W}_k^h
                \end{align*}
                Then, each head can be written as:
                \[
                    \textbf{Sa}_h[\textbf{X}]=\textbf{Softmax}\left(\frac{\textbf{Q}_h^{\top}\textbf{K}_h}{\sqrt{D_k^h}}\right)\textbf{V}_h
                \]
                The multi-head attention is defined as follows;
                \[
                    \textbf{MhSA}[\textbf{X}] = [\textbf{Sa}_1[\textbf{X}], \dots, \textbf{Sa}_H[\textbf{X}]]\textbf{W}
                \]
                where \textbf{W} is another weight matrix, and $H$ is the number of heads.
            \end{defn}
            If the number of heads is $H$, each $D_v$ is usually chosen to be equal to $D/H$.

        \subsubsection{Positional Encoding}
            As the structure of the attention mechanism shows, the attention mechanism itself is equivariant to
            permutation of input values. However, the sequential information is important in NLP. To overcome this,
            we can inject a positional information into the input itselt, without modifying the attention mechanism.


\end{document}